Verification of the CVM algorithm with a Functional Probabilistic Invariant

### 2025-06-30 paper/sec/original_proof.tex
minor edit

To handle these situations we generalized \cref{o:sample_distrib} to allow for the case where the index $J$ splitting the set of coin flips $f$ and $g$ depend on, may itself depend on the result of $f$.
%It is possible to express the above in a point-free manner using the reader monad.
%This is a deterministic monad, which provides a read operation to a global value, such as our set of coin flips.
%(In Haskell, the reader monad is commonly used to provide a fixed environment to algorithms, such as global configuration options, paths or command lines parameters~\cite{jones1995}.)
%
%\begin{isabelle_cm}
%\isacommand{datatype}\ \isacharparenleft{\isacharprime}c\isacharcomma\ {\isacharprime}a\isacharparenright\ reader{\isacharunderscore}monad\ =\ Reader\ {\isacharparenleft}run{\isacharunderscore}reader\isacharcolon\ \isacartoucheopen{\isacharprime}c\ \isasymRightarrow\ {\isacharprime}a\isacartoucheclose\isacharparenright)\isanewline
%\isanewline
%\isacommand{definition}\ bind{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}bind{\isacharunderscore}rd\ m\ f\ \isacharequal\ Reader\ \isacharparenleft{\isasymlambda}r\isachardot\ run{\isacharunderscore}reader\ {\isacharparenleft}f\ {\isacharparenleft}run{\isacharunderscore}reader\ m\ r\isacharparenright\isacharparenright\ r\isacharparenright\isacartoucheclose\isanewline
%\isacommand{definition}\ return{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}return{\isacharunderscore}rd\ x\ \isacharequal\ Reader\ \isacharparenleft{\isasymlambda}{\isacharunderscore}\isachardot\ x\isacharparenright\isacartoucheclose\isanewline
%\isacommand{definition}\ get{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}get{\isacharunderscore}rd\ x\ \isacharequal\ Reader\ id\isacartoucheclose
%\end{isabelle_cm}
%With the definition above, we can define our sampling function with respect to the reader monad, where the environment is the entire set of coin flips, which is now a monad morphism (from the reader monad to the Giry monad):
%\begin{isabelle_cm}
%  sample{\isacharunderscore}rd\ \isacharequal\ sample\ \isasymcirc\ run{\isacharunderscore}reader
%\end{isabelle_cm}

>>>>

To handle these situations we generalized \cref{o:sample_distrib} to allow for the case where the set of indices $J$ splitting the set of coin flips $f$ and $g$ depend on, may itself depend on the result of $f$.
%It is possible to express the above in a point-free manner using the reader monad.
%This is a deterministic monad, which provides a read operation to a global value, such as our set of coin flips.
%(In Haskell, the reader monad is commonly used to provide a fixed environment to algorithms, such as global configuration options, paths or command lines parameters~\cite{jones1995}.)
%
%\begin{isabelle_cm}
%\isacommand{datatype}\ \isacharparenleft{\isacharprime}c\isacharcomma\ {\isacharprime}a\isacharparenright\ reader{\isacharunderscore}monad\ =\ Reader\ {\isacharparenleft}run{\isacharunderscore}reader\isacharcolon\ \isacartoucheopen{\isacharprime}c\ \isasymRightarrow\ {\isacharprime}a\isacartoucheclose\isacharparenright)\isanewline
%\isanewline
%\isacommand{definition}\ bind{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}bind{\isacharunderscore}rd\ m\ f\ \isacharequal\ Reader\ \isacharparenleft{\isasymlambda}r\isachardot\ run{\isacharunderscore}reader\ {\isacharparenleft}f\ {\isacharparenleft}run{\isacharunderscore}reader\ m\ r\isacharparenright\isacharparenright\ r\isacharparenright\isacartoucheclose\isanewline
%\isacommand{definition}\ return{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}return{\isacharunderscore}rd\ x\ \isacharequal\ Reader\ \isacharparenleft{\isasymlambda}{\isacharunderscore}\isachardot\ x\isacharparenright\isacartoucheclose\isanewline
%\isacommand{definition}\ get{\isacharunderscore}rd\ \isacommand{where}\ {\isacartoucheopen}get{\isacharunderscore}rd\ x\ \isacharequal\ Reader\ id\isacartoucheclose
%\end{isabelle_cm}
%With the definition above, we can define our sampling function with respect to the reader monad, where the environment is the entire set of coin flips, which is now a monad morphism (from the reader monad to the Giry monad):
%\begin{isabelle_cm}
%  sample{\isacharunderscore}rd\ \isacharequal\ sample\ \isasymcirc\ run{\isacharunderscore}reader
%\end{isabelle_cm}
